\section{Python AIMA}

\begin{enumerate}
    \item In order to perform a search, what are the classes that you
        must define or extend? Explain precisely why and where they are
        used inside a tree\_search.
    \item In the expand method of the class Node what is the advantage
        of using a yield instead of building a list and returning it
        afterwards ?
    \item Both breadth\_first\_graph\_search and depth\_first\_graph\_search
        are making a call to the same function. How is their fundamental
        difference implemented?
    \item What is the difference between the implementation of the
        graph\_search and the tree\_search methods and how does it impact
        the search methods ?
    \item What kind of structure is used to implement the closed list?
        What are the methods involved in the search of an element inside
        it? What properties must thus have the elements that you can put
        inside the closed list ?
    \item How technically can you use the implementation of the closed
        list to deal with symmetrical states ? (hint: if two symmetrical
        states are considered by the algorithm to be the same, they will
        not be visited twice)
\end{enumerate}

\section{The Numberlink Problem}

\begin{enumerate}
    \item Explain the advantages and weaknesses of the following search
        strategies on this problem (not in general): depth first,
        breadth first.
    \item How can we exploit the uniqueness of solution to reduce the
        search space? Why is the method pathExists useful ?
    \item Is the order in which we choose the paths important? How can
        we use this to reduce the search space? When starting a new
        path, we can choose to start with any of its two endpoint. How
        should this choice be done ?
    \item What are the advantages and disadvantages of using the tree
        and graph search for this problem. Which approach would you
        choose? Which approach allows you to avoid expending twice
        symmetrical states ?
    \item Implement this problem in Python 3. Extend the Problem class
        and implement the necessary methods and other class(es) if
        necessary. Your file must be named numberlink.py. You program
        must take as only input the path to the init file of the problem
        to solve. It must print to the standard output a solution to the
        problem satisfying the above format. Your file must be encoded
        in utf-8. Submit your program on INGInious.
    \item Experiments must be realized with the 10 instances of the
        numberlink problem provided. Report in a table the results on
        the 10 instances for depth-first and breadth- first strategies
        on both tree and graph search (4 settings). You must report the
        time, the number of explored nodes and the number of steps from
        root to solution. When no solution can be found by a strategy in
        a reasonable time (3 min), explain the reason (time-out and/or
        swap of the memory). What do you conclude from those experiments
        ?
\end{enumerate}
